\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Articles}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
This document is filled with different articles that we found interesting and wanted to bookmark for the future.

\section{Articles}
\subsection{Mathematics}
The Most Dangerous Equation, http://assets.press.princeton.edu/chapters/s8863.pdf
\begin{itemize}
    \item A paper about De Moivre's equation on the standard deviation of the sampling distribution of the mean. 
  The equation shows the relation between sample size and variance.
\end{itemize}


\subsection{Better Code}
Seven Ineffective Coding Habits of Many Programmers, https://www.youtube.com/watch?v=ZsHMHukIlJY
\begin{itemize}
    \item An Istambul Tech Talks talk about tips and refactoring steps on reducing code complexity.
\end{itemize}


\subsection{Machine Learning}
Avoiding side effects in complex environments, https://www.lesswrong.com/posts/5kurn5W62C5CpSWq6/avoiding-side-effects-in-complex-environments
\begin{itemize}
\item How reward functions can be modified to avoid trickery.
\end{itemize}  
Gaussian processes for dummies, http://katbailey.github.io/post/gaussian-processes-for-dummies/
\begin{itemize}
\item "[A] very basic intro to Gaussian Processes".
\end{itemize} 
Random Search for Hyper-Parameter Optimization, https://jmlr.csail.mit.edu/papers/volume13/bergstra12a/bergstra12a.pdf
\begin{itemize}
\item Why random search is better than grid search for finding good Hyper-Parameter configurations.
\end{itemize} 

\subsection{Productivity/Enterprise}
The makersschedule, http://www.paulgraham.com/makersschedule.html
\begin{itemize}
\item A blog post about the differences in schedule between makers and managers.
\end{itemize} 

\subsection{Papers I still want to read}
Cognitive Complexity, https://www.sonarsource.com/docs/CognitiveComplexity.pdf
\begin{itemize}
\item A white paper about "[a] new way of measuring [the] understandability" of your code automatically.
\end{itemize} 

\bibliographystyle{plain}
\bibliography{references}
\end{document}
